Length Gauge Theory of Surface Second Harmonic Generation

### 2014-11-17 intro.tex
corrected accent on Mejia in intro

Concerning the optical response of surfaces and interfaces,
Mendoza and Moch\'an\cite{mendozaPRB96} produced an early review of 
theoretical SHG spectra from surfaces. 
Arzate and Mendoza\cite{arzatePRB01} improved upon that work and
went into a detailed analysis of the different contributions to the 
SHG spectra of a surface and the nuanced relationship between bulk, 
surface, interband, intraband, $1\omega$ and $2\omega$ terms. 
Calculated surface SHG spectra using these schemes coincide with experimental
results in both the velocity gauge
\cite{mendozaPRB01,mendozaPRL98,reiningPRB94} and the length gauge approach
\cite{sharmaPRB03}. 
Perhaps of more relevance to this work, 
Mendoza \emph{et al}.\cite{mendozaPRB06} and 
Mejía \emph{et al}.\cite{mejiaRMF04} developed a layer-by-layer analysis for 
the linear and nonlinear responses of semiconductor systems. This model
allows for obtaining results from selected regions within a slab or bulk,
including the surface.
More recently, 
Trolle \emph{et al}.\cite{trollePRB14} 
elaborate on a new theoretical model for surface SHG of 
mono-layer MoS$_{2}$. Their approach is based on the tight-binding model 
fitted to GW results and include excitonic effects from the 
Bethe-Salpeter exciton picture. However, this new model is not 
\emph{ab initio} and has no consideration for a layered approach.

>>>>

Concerning the optical response of surfaces and interfaces,
Mendoza and Moch\'an\cite{mendozaPRB96} produced an early review of 
theoretical SHG spectra from surfaces. 
Arzate and Mendoza\cite{arzatePRB01} improved upon that work and
went into a detailed analysis of the different contributions to the 
SHG spectra of a surface and the nuanced relationship between bulk, 
surface, interband, intraband, $1\omega$ and $2\omega$ terms. 
Calculated surface SHG spectra using these schemes coincide with experimental
results in both the velocity gauge
\cite{mendozaPRB01,mendozaPRL98,reiningPRB94} and the length gauge approach
\cite{sharmaPRB03}. 
Perhaps of more relevance to this work, 
Mendoza \emph{et al}.\cite{mendozaPRB06} and 
Mej\'ia \emph{et al}.\cite{mejiaRMF04} developed a layer-by-layer analysis for 
the linear and nonlinear responses of semiconductor systems. This model
allows for obtaining results from selected regions within a slab or bulk,
including the surface.
More recently, 
Trolle \emph{et al}.\cite{trollePRB14} 
elaborate on a new theoretical model for surface SHG of 
mono-layer MoS$_{2}$. Their approach is based on the tight-binding model 
fitted to GW results and include excitonic effects from the 
Bethe-Salpeter exciton picture. However, this new model is not 
\emph{ab initio} and has no consideration for a layered approach.
